% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
\usepackage{multicol}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\ResumeAuthor}{Megan Will}
\newcommand{\ResumeTitle}{Megan Will's Resume}
\newcommand{\ResumeNote}{Resume compiled on {\today}}
\newcommand{\ResumeWebpage}{https://github.com/megwill4268}

% PDF settings and properties.
\hypersetup{
pdftitle={\ResumeTitle},
pdfauthor={\ResumeAuthor},
pdfsubject={\ResumeWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\ResumeAuthor}
\begin{SubTitle}
\href{mailto:megan.will88@gmail.com}{megan.will88@gmail.com}
https://github.com/megwill4268
\,\SubBulletSymbol\,
+1\,(512)\,626-4315
\end{SubTitle}
\begin{Body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Pertinent Experience   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Pertinent Experience}
{Pertinent Experience}
{PDF:Pertinent Experience}

\Entry
\href{http://www.utexas.edu/}
{\textbf{University of Texas at Austin}},
ITS Apps Middleware Team 

\Gap
\BulletItem
Software Engineer
\hfill
\DatestampYM{2016}{08} -- Current
\begin{Detail}
\SubBulletItem
Technical lead for Central UT Stonebranch Workload Automation and Central UT Message Broker (RabbitMQ), Co-Technical lead for Urgent Email  (Duties: assessing service state, keeing upgraded and secure, providing user support and consultations)
\SubBulletItem
Ported Puppet app configuration management scripts to Ansible for Message Broker to streamline upgrades and maintenance. 
\SubBulletItem
Added an extension to the university's custom Python/Dango web platform to allow for custom worker deployment and integration with Message Broker. (Python, Systemd, Heroku style procfiles).
\SubBulletItem
Wrote Java notification feed for employee/student data changes to be brokered by RabbitMQ and consumed by different business areas. 
\SubBulletItem
Consulted with UT International office to ensure a robust and secure implementation of acquired Cold Fusion app on Windows.
\SubBulletItem
Created a Python package to simplify common LDAP queries to the university LDAP directory. 
\SubBulletItem
Helped mentor other developers in how to turn SVN externals into packages and use a binary repository in migrating repos from SVN/GIT. 
\end{Detail}

\Gap
\BulletItem
Middleware Engineer
\hfill
\DatestampYM{2016}{03} --
\DatestampYM{2016}{08}
\begin{Detail}
\SubBulletItem
Technical Lead implementing central Message Broker offering (RabbitMQ), contributed to Puppet-rabbitmq module, wrote application and server configuration, performed and designed load and stress testing. 
\SubBulletItem
Wrote and designed an application to allow users to manage Message Broker permissions for their vhost only (Python Django app with a MYSQL backend, syncing to Message Broker via API, batch deprovisioning, full test suite).
\SubBulletItem
Created, presented and distributed demo of Message Broker tutorial vm (Ubuntu w/Ansible provisioning) illustrating near real time messaging integrating 4 processes, two Python/Django apps, a Ruby app, and a Jython app.
\end{Detail}

\Gap
\BulletItem
Software Developer 
\hfill
\DatestampYM{2015}{02} --
\DatestampYM{2016}{02}
\begin{Detail}
\SubBulletItem
Created and distrubuited a bundle of Python/Django and other Python libraries for deployment and development on the university's custom Python/Django web platform.
\SubBulletItem
Upgraded local development vm and Python bundles from 32bit to 64bit for university's custom Python/Django web platform developers.
\SubBulletItem
Wrote bash utility to find number of deployed applications on the custom Python/Django web platform utilizing any given Python library and initiated retirement of unused out of support libraries.
\end{Detail}

\Gap
\BulletItem
Software Developer Trainee
\hfill
\DatestampYM{2014}{09} --
\DatestampYM{2015}{02}
\begin{Detail}
\SubBulletItem
Learned Python, Django, HTML, CSS, Natural, project management and design skills.
\end{Detail}


%%%%%%%%%%%%%%%%%%
%% Beyond  Work %%
%%%%%%%%%%%%%%%%%%

\Section
{Beyond Work}
{Beyond Work}
{PDF:Beyond Work}

\Entry
\href{https://djangogirls.org/austin/}
{\textbf{Django Girls}},
Austin, TX

\Gap
\BulletItem
Coordinator
\hfill
\DatestampYM{2016}{08} --
Current
\begin{Detail}
\SubBulletItem
Organized Django Girls Austin teaching Python tutorials and Python Challenge for The Girl Scouts of Central Texas STEM Hackathon (March 2017). 
\SubBulletItem
\href{https://www.gitbook.com/book/megwill4268/learning-python-on-mars/details}{\text{Wrote Python games and co-wrote tutorials for the Hackathon. }}
\SubBulletItem
Co-organized Django Girls Workshop December 3, 2016, providing a free workshop through Rackspace to help women interested in careers in technology.
\end{Detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Other Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}

\Gap
\BulletItem
Office Coordinator, Epic Health Services 
\hfill
\DatestampYM{2013}{07} --
\DatestampYM{2014}{08}
\BulletItem
Client Service Coordinator, Epic Health Services 
\hfill
\DatestampYM{2012}{10} --
\DatestampYM{2013}{06}
\BulletItem
Business Office Specialist I, Health Sense Homecare 
\hfill
\DatestampYM{2012}{07} --
\DatestampYM{2013}{10}
\BulletItem
Receptionist, Health Sense Homecare
\hfill
\DatestampYM{2012}{04} --
\DatestampYM{2012}{07}
\BulletItem
Front Desk Clerk, Embassy Suites
\hfill
\DatestampYM{2011}{07} --
\DatestampYM{2012}{04}



%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}


\Entry
\textbf{Configuration Management:}
Ansible, Puppet
\Entry
\textbf{Operating Systems:}
Linux (Redhat/ Ubuntu)
\Entry
\textbf{Integration Tools:}
Message Broker, ESB (API management), Workload Automation 
\Entry
\textbf{Formal Languages:}
Java (basic), Python (advanced), Ruby (basic), bash, willing to learn the rest
\Entry
\textbf{Basic Utilites:}
Git/ SVN, Binary repositories, Jmeter, Docker, Virtual Machines/Vagrant

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}


\Entry
\textbf {Centre College}
\hfill
\DatestampYM{2007}{08} --
\DatestampYM{2011}{05}
\BulletItem
Bachelors of Arts with Majors in French and Spanish
\BulletItem
Lettered in Track and Cross Crountry as distance runner
\end{Body}
\end{document}